Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-04-15 Scripts/Initial_Analysis.Rmd
Function working (mechanically) in carmelia

    for(i in 1:length(Ids)){

      EEZ_ids <- Neighbours_combo %>% 
        filter(neighbour_id == Ids[i])

@@

      if(i == 1){
        f_df <- Final_Result
      }else{
        f_df <- bind_rows(f_df,Final_Result)
      }
    }

    return(f_df)

@@

    f_df <- tibble(
      taxon_key = Spp,
      eez_name = NA,
      emerging_yr = NA
    )

@@

  return(f_df)

@@

#  #One spp works 
# suppressMessages(
# x <-  TransIndex(Spp = 600245,
#              year,
#              data_type = "Catch",
#              ensamble_list,
#              path,
#              Neighbours = Neighbours,
#              eez_centroid)
# )
# Multiple spp

@@

spp_list <- c(600004,
              600005,
              600245,
              600006
              )

@@

suppressMessages(
  suppressWarnings(
    Test <- bind_rows(
      lapply(spp_list,
             TransIndex,
             year,
             data_type = "Catch",
             ensamble_list,
             path,
             Neighbours,
             eez_centroid
      )
    )
  )
)

@@

>>>>

  corefx <- function(Ids){

      EEZ_ids <- Neighbours_combo %>% 
        filter(neighbour_id == Ids)

@@

      # if(i == 1){
      #   f_df <- Final_Result
      # }else{
      #   f_df <- bind_rows(f_df,Final_Result)
      # }
    return(Final_Result)
      }

  x <- bind_rows(
    mclapply(Ids,corefx)
  )
    # return(f_df)

@@

    x <- tibble(
      taxon_key = Spp,
      eez_name = NA,
      emerging_yr = NA
    )

@@

  return(x)

@@

#  #One spp works 
# suppressMessages(
# TransIndex(Spp = 600006,
#              year,
#              data_type = "Catch",
#              ensamble_list,
#              path,
#              Neighbours = Neighbours,
#              eez_centroid)
# Multiple spp

@@

spp_list <- c(600004,
              600005,
              600245#,
              # 600006
              )

@@

suppressMessages(
  suppressWarnings(
    Test <- bind_rows(
      mclapply(spp_list,
             TransIndex,
             year,
             data_type = "Catch",
             ensamble_list,
             path,
             Neighbours,
             eez_centroid
      )
    )
  )
)

@@

# Version 1 (embeded loop) <- 3.01
# Version 2 (embeded lapply) <- 2.71
# Version 3 (embeded mclapply) <- 1.597311 mins
# Version 4 (embeded mclapply) + mclapply in spp <- 1.597311 mins
